 Solving ODEs in R

### 2014-12-19 documentation/interactive_kefi_2007_bifurcation.Rmd
update model exploration

inputPanel(
  sliderInput("m", label = "plant mortality:",
              min = 0.0, max = 1, value = 0.25, step = 0.01),
  sliderInput("c", label = "competition:",
              min = 0.0, max = 1, value = 0.2, step = 0.01),
  sliderInput("delta", label = "seed distpersal:",
              min = 0.0, max = 1, value = 0.9, step = 0.01),
  sliderInput("f", label = "facilitation:",
              min = 0.0, max = 1, value = 0.9, step = 0.01), 
  sliderInput("r", label = "regeneration rate:",
              min = 0.0, max = 1, value = 0.01, step = 0.01), 
  sliderInput("d", label = "degradation rate:",
              min = 0.0, max = 1, value = 0.1, step = 0.01)
)

@@

plot(output$rho_p ~ iterations$b, type = "l", ylim = c(0,1))

@@

lines(output$rho_p ~ iterations$b)

>>>>

inputPanel(
  sliderInput("m", label = "plant mortality:",
              min = 0.0, max = 1, value = 0.25, step = 0.01),
  sliderInput("c", label = "competition:",
              min = 0.0, max = 1, value = 0.2, step = 0.01),
  sliderInput("delta", label = "seed dispersal:",
              min = 0.0, max = 1, value = 0.9, step = 0.01),
  sliderInput("f", label = "facilitation:",
              min = 0.0, max = 1, value = 0.9, step = 0.01), 
  sliderInput("r", label = "regeneration rate:",
              min = 0.0, max = 1, value = 0.01, step = 0.01), 
  sliderInput("d", label = "degradation rate:",
              min = 0.0, max = 1, value = 0.1, step = 0.01)
)

@@

plot(output$rho_p ~ iterations$b, type = "p",pch  =20, ylim = c(0,1))

@@

points(output$rho_p ~ iterations$b, pch = 20)

### 2014-12-19 documentation/solving_ODEs.Rmd
update model exploration

>>>>

## Mortality vs Growth (simulated)

It would be great to solve the equation system into a function of vegetation cover, $\rho_+$, if this is possible.

```{r}
output_high$M <- output_high$rho_p * model_parms$m
output_high$G <- with(output_high, (rho_p * model_parms$delta + (1 - model_parms$delta ) * (rho_p - rho_pm - rho_pp)/(1-rho_p*rho_m))*(model_parms$b - model_parms$c * rho_p)*(1-rho_p-rho_m)  )

plot( output_high$G ~ output_high$rho_p,
      type = "l",
      xlim = c(0,1) )

lines(  output_high$M ~ output_high$rho_p, type = "l")
